Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-16 main.Rmd
where $z$ is the index of the bottom granularity $kin$
finite number of spans of time

Granularities can also be periodic with respect to other granularities, _"except for a finite span of time where they behave in an anomalous way"_; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

>>>>

Granularities can also be periodic with respect to other granularities, _"except for a finite number of spans of time where they behave in an anomalous way"_; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

, where $z$ is the index of the bottom granularity $kin$.
